Clustering time series based on probability distributions across temporal granularities

### 2021-11-01 main.Rmd
keywords update

keywords:
- data visualization
- statistical distributions
- time granularities
- calendar algebra
- periodic data
- grammar of graphics
- R

>>>>

keywords:
- clustering
- time granularities
- probability distributions
- Jensen-Shannon distances
- periodic data
- smart meter
- electricity consumption behaviour
- R
